\section{Conclusion}
\label{sec:Conclusion}
\lhead{Conclusion}

This report has covered the details of the working conditions of the SOFA project of the authors. To do so, the major parts of project management were discussed and it was detailed how each part is to be handled over the course of the project and how it might influence the work flow and outcome of said project.
\newline
It has shows that not all parts of project management are necessarily applicable to the SOFA project in question. Given the educational nature of the project, topics such as cost and budget management are not as relevant as others and have been dealt with mostly for the sake of completeness.
\newline
However, by dealing with all topics regarding project management, the project group is now able to have a clear definition of the project and the all the tasks that are meant to be part of it. It is defined how the project group will work on the project, including the tools to use and the communication that has to be upheld.
\newline
Very important is the breakdown of the project's deliverable product, which is now a lot more accessible to the development team, as it is now defined which parts of the product belong together and what functionality is ultimately supposed to be developed.
\newline
The project team is confident that the project can be executed successfully, in parts thanks to the development plan as it is defined in this document. At the time of writing the team has already started with the development of the product and will use this document for future reference.