\section{Procurement Management}
\label{sec:procurement}
\lhead{\thesection \space Procurement Management}

Part of the Project Management process is to manage the processes necessary to acquire services and products that ensure the ability to work on the project. This includes both management services as well as external software products used in development.
\newline
The project encompasses the following products and services. It is detailed how they will be used in the project and who is responsible for providing them.

\subsection{Atlassian Jira}

To manage the agile process of the project, Jira by Atlassian will be made use of. The platform allows the project team members to keep track of the backlog of tasks and user stories and to manage them in Scrum sprints.
\newline
Jira is being provided by the client \textit{Connected.Football}. The client is responsible for granting the other team members and stakeholders access to the tool and to ensure that certain team members have the necessary permissions to interact with the provided tool set. The developing team members are responsible for keeping the content of the created Jira boards correct and up-to-date.

\subsection{Github}

The developed \textit{React Native} product is being versioned using \textit{Git}, which uses Github as a platform. The client is again responsible for providing the team members access to the versioning system and to ensure that the provided sources are in a state that enables development by the project team.
\newline
The project team is responsible for committing changes they make to the product to the Github repository, including accurate descriptions of what has been changed since the last commit. It is also the responsibility of the team to resolve commit errors and conflicts, as well as to minimize the likelihood of such occurrences.

\subsection{Subversion}

Another versioning system used over the course of the project is Subversion. This system will be used to commit and share University-related artifacts and documents, such as this project plan.
\newline
Fontys Hogeschool Techniek en Logistiek Venlo is responsible for the availability and integrity of the repositories in question. Again, it is the responsibility of the team members to ensure a working state of the repositories and to commit changes with accurate descriptions.

\subsection{Firebase}

Some backend functionality of the product is relying on Google's \textit{Firebase}. It is for example used to send push notifications to mobile user devices.
\newline
It is the responsibility of the client to ensure that the project team has the necessary rights to interact with the already set up \textit{Firebase} backend. On the other hand, the team is responsible for interacting with the backend in a proper way, ensuring the integrity of the provided data and infrastructure.

\subsection{Integrated development environments}

The project team uses some integrated development environments (IDEs) to develop the product, most notably \textit{Visual Studio Code}. The IDE is used to inspect and change the source code of the product.
\newline
The developer is responsible for the functionality of the IDE. The team is able to use the IDEs as they are all provided through open source. It is their responsibility to use the IDE as intended and to figure out how to resolve errors in the event that they occur.

\subsection{Node Modules}

The product used various \textit{Node} modules to offer functionality in the product. These modules are available from various node repositories.
\newline
The developers of the \textit{Node} modules are responsible for the development of the \textit{Node} modules themselves and for the documentation that comes with them. Since the modules are published as open source, the project team should be prepared that errors might occur while using them. They are furthermore responsible for implementing the usage of the modules in the product as the developer intended and documented.
\newline
Some of the \textit{Node} modules are developed by the client. Their integrity is therefore their responsibility.

\subsection{Slack}

The development team uses \textit{Slack} to communicate outside of personal meetings, both in communication with each other as well as with the client. It is also used to share information, such as documents and source code snippets, in a non-persistent way.
\newline
The availability of the application is ensured by the developer. It is the responsibility of the client to enable that the development team is able to join and use the \textit{Slack} platform. The project team has the responsibility to not share any sensitive information, such as credentials, over this platform.

%\subsection{Conduct Procurement}
%\subsection{Control Procurement}
%\subsection{Close Procurement}